### 2017-01-13 Plos-one-manuscript/latex/manuscript.tex
started nature comm manuscript

Our printed pipette improves on existing open design pipettes in several ways. 
Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
The pipette can be adjusted to any discrete volume within range.
In addition, the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
Unlike existing designs our design does not use a membrane that may wear out and require tedious replacement.
The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.

This design relies heavily on the syringe, a specialized part, for the core function as well as accuracy.
Fortunately, as disposable syringes are a regulated medical device they must meet high standards making them a reliable part for this design.
As good as the performance of our printed pipette is, a commercial pipette should be expected to be more reliable and preferred for critical procedures. 
Adjusting our printed pipette to the desired volume requires more time and attention which would be tedious for procedures requiring many adjustments.
On the other hand, due to the \$6 cost to make, many printed pipettes could be assembled and pre-set, each for a planned transfer, rather then re-adjusting one commercial pipette for each step.
The printable pipette can also be used as a disposable, sparing the commercial micropipette, in situations were cross-contamination and resterilization is required, or damage from volatile reagents is a concern.
This pipette would also be ideal for high school and teaching labs or any resource limited program especially as part of a module about 3D printing.

>>>>

Our printed pipette improves on existing open design pipettes in several ways. 
Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
The pipette can be adjusted to any discrete volume within range.
In addition, the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
Unlike existing designs our design does not use a membrane that may wear out and require replacement.
The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.

Our design relies heavily on the syringe, a specialized part, for the core function as well as accuracy.
Fortunately, as disposable syringes are a regulated medical device they must meet high standards making them a reliable part for this design.
As good as the performance of our printed pipette is, a commercial pipette should be expected to be more reliable and preferred for critical procedures. 
Adjusting our printed pipette to the desired volume requires more time and attention which would be tedious for procedures requiring many adjustments.
On the other hand, due to the \$6 cost to make, many printed pipettes could be assembled and pre-set, each for a planned transfer, rather then re-adjusting one commercial pipette for each step.
The printable pipette can also be used as a disposable, sparing the commercial micropipette, in situations were cross-contamination and resterilization is required, or damage from volatile reagents is a concern.
This pipette would also be ideal for high school and teaching labs or any resource limited program.
